**Preprinting Microbiology**

### 2017-04-17 submission/Schloss_PrePrints_mBio_2017.Rmd
Add protist as a microbiology-related search term

***Metrics for microbiology-affiliated preprints.*** To analyze the use of preprints, I downloaded the *bioRxiv* on December 31, 2016. I chose to analyze *bioRxiv* preprints because these preprints are amenable for submission to ASM journals and there were `r nrow(biorxiv)` *bioRxiv* preprints compared to the 2,650 available at *PeerJ Preprint*. Among the `r nrow(biorxiv)` preprints on bioRxiv, `r sum(biorxiv$category=="Microbiology", na.rm=T)` were assigned by the authors into the Microbiology category. One limitation of the *bioRxiv* interface is the inability to assign manuscripts to multiple categories or to tag the content of the preprint. For example, this manuscript could be assigned to either the Microbiology or the Scientific Communication and Education categories. To counter this limitation, I developed a more permissive approach that classified preprints as being microbiology-affiliated if their title or abstract had words containing *yeast*, *fung*, *viral*, *virus*, *archaea*, *bacteri*, *microb*, *microorganism*, or *pathogen*. I identified `r sum(non_micro_micro, na.rm=T)` additional manuscripts that I considered microbiology-affiliated. These microbiology-affiliated preprints were primarily assigned to the `r non_micro_category_names[1]` (N=`r non_micro_category_counts[1]`), `r non_micro_category_names[2]` (N=`r non_micro_category_counts[2]`), or `r non_micro_category_names[3]` (N=`r non_micro_category_counts[3]`) categories.

>>>>

***Metrics for microbiology-affiliated preprints.*** To analyze the use of preprints, I downloaded the *bioRxiv* on December 31, 2016. I chose to analyze *bioRxiv* preprints because these preprints are amenable for submission to ASM journals and there were `r nrow(biorxiv)` *bioRxiv* preprints compared to the 2,650 available at *PeerJ Preprint*. Among the `r nrow(biorxiv)` preprints on bioRxiv, `r sum(biorxiv$category=="Microbiology", na.rm=T)` were assigned by the authors into the Microbiology category. One limitation of the *bioRxiv* interface is the inability to assign manuscripts to multiple categories or to tag the content of the preprint. For example, this manuscript could be assigned to either the Microbiology or the Scientific Communication and Education categories. To counter this limitation, I developed a more permissive approach that classified preprints as being microbiology-affiliated if their title or abstract had words containing *yeast*, *fung*, *viral*, *virus*, *archaea*, *bacteri*, *microb*, *microorganism*, *pathogen*, or *protist*. I identified `r sum(non_micro_micro, na.rm=T)` additional manuscripts that I considered microbiology-affiliated. These microbiology-affiliated preprints were primarily assigned to the `r non_micro_category_names[1]` (N=`r non_micro_category_counts[1]`), `r non_micro_category_names[2]` (N=`r non_micro_category_counts[2]`), or `r non_micro_category_names[3]` (N=`r non_micro_category_counts[3]`) categories.
